### 2011-11-19 doc/theses/vitasek/chapter-6-conclusion.tex
Thesis: before merging reviews.

To the best of our knowledge, at the time of writing this work is our approach to finding \texttt{ID} attributes the best one known.

>>>>

To the best of our knowledge, at the time of writing this work is our approach to finding \texttt{ID} attributes the best one known.\\

The wisdom found in the experiments in this work might be the following. While it is important to be able to write a heuristic algorithm tailored to the specific problem being solved, such as the authors of \cite{fidax} did, it should be noted that sometimes it is better to solve a more generalized problem. In this case the transformation to MIP formulation and using a dedicated solver proved to produce better results in shorter time.

### 2011-11-19 doc/theses/vitasek/diplomka.tex
Thesis: before merging reviews.

\noindent
I would like to thank everyone participating in the jInfer project for creating a~solid foundation for this work, namely Irena Mlýn\-ko\-vá, Mi\-chal Klem\-pa, Má\-rio Mi\-ku\-la, Ro\-bert Sme\-ta\-na and Mi\-chal Švi\-rec. The thanks goes again to Ms. Mlýn\-ko\-vá for supervising this work, as well as everyone reviewing it, in no~particular order Lý\-dia Šva\-ger\-ko\-vá, Mi\-chal Šva\-ger\-ka, Zu\-za\-na Ma\-sá\-ro\-vá, Mi\-chal Ke\-se\-ly and others\textsuperscript{HB}.

@@

\newpage
\phantomsection
\addcontentsline{toc}{chapter}{Bibliography}
%\nocite{*}
%\bibliographystyle{alpha}
%\bibliography{literature}
	\include{bibliography}

>>>>

\noindent
I would like to thank everyone participating in the jInfer project for creating a~solid foundation for this work, namely Irena Mlýn\-ko\-vá, Mi\-chal Klem\-pa, Má\-rio Mi\-ku\-la, Ro\-bert Sme\-ta\-na and Mi\-chal Švi\-rec. The thanks goes again to Ms. Mlýn\-ko\-vá for supervising this work, as well as everyone reviewing it, in no~particular order Lý\-dia Šva\-ger\-ko\-vá, Mi\-chal Šva\-ger\-ka, Zu\-za\-na Ma\-sá\-ro\-vá, Mi\-chal Ke\-se\-ly and others\textsuperscript{HV}.

@@

\newpage
\phantomsection
\addcontentsline{toc}{chapter}{Bibliography}
\nocite{*}
\bibliographystyle{alpha}
\bibliography{literature}
%	\include{bibliography}
